Novel Sampling Using Stochastic Gradient Descent

### 2016-12-05 poster/main.tex
update last column

\begin{block}{SGD As Posterior Sampler}
When $p(\theta)$ is the posterior distribution of some parameters given a set of data $X_1,\ldots, X_n$, i.e.,
\[
p(\theta) = \prod_{i=1}^n P(X_i|\theta) P(\theta),
\]
The noisy gradient step in Algorithm 1 can be estimated by subsampling:
\begin{theorem}[Central limit theorem]
Let $K$ be the subsampling size and $\eta_1,\ldots, \eta_K$ be samples drawing from $1,\ldots, n$ with replacement, then
\[
K^{-1}\sum_{i=1}^K (\nabla \log P(X_{\eta_i}|\theta^t) - \log P(\theta^t)) \sim \N(n^{-1} \nabla \log p(\theta) , K^{-1}\cov \nabla \log p(\theta)).
\]
\end{theorem}

@@

\begin{figure}
\includegraphics[width=0.5\linewidth]{../figure/simulation2_empirical.png}
\includegraphics[width=0.5\linewidth]{../figure/simulation2_real.png}
\caption{Figure caption}
\end{figure}

@@

\begin{block}{Upper Bound On Mixing Time}
Mixing time correspon

@@

\begin{itemize}
\item Proposed fast SGD sampler for posterior distributions. Computing the likelihood from the full data is intensive.
\item Proved accurate stationary distribution based on oracle results
\item Established connection between SGD and maximize \emph{a posteriori} (MAP)
\item Derived upper bound on mixing time
\item Future work: Finite sample rates of convergence for the mixing time
\end{itemize}

@@

\begin{block}{Contant Information}

>>>>

\begin{block}{SGD As Fast Posterior Sampler}
When $p(\theta)$ is the posterior distribution of some parameters given a set of data $X_1,\ldots, X_n$, i.e.,
\[
p(\theta) = \prod_{i=1}^n P(X_i|\theta) P(\theta),
\]
The noisy gradient step in Algorithm 1 can be estimated by subsampling:
\begin{theorem}[Central limit theorem]
Let $K$ be the subsampling size and $\eta_1,\ldots, \eta_K$ be samples drawing from $1,\ldots, n$ with replacement, then
\[
K^{-1}\sum_{i=1}^K (\nabla \log P(X_{\eta_i}|\theta^t) - \log P(\theta^t)) \sim \N(n^{-1} \nabla \log p(\theta) , K^{-1}\cov \nabla \log p(\theta)).
\]
\end{theorem}

@@

\begin{figure}
\includegraphics[width=0.5\linewidth]{../figure/simulation2_empirical.png}
\includegraphics[width=0.5\linewidth]{../figure/simulation2_real.png}
\caption{The empirical/real density for $(\mu, \sigma^2)$ where $p(X_1|\mu, \sigma^2)\sim \N(\mu, \sigma^2)$, data $X_1,\ldots, X_{1000}$ is drawn from $\N(0, 1)$, $K = 1000$, sample size is $1000$. The empirical density is close to the real density. Note that variance $\sigma^2$ has higher variance than the expectation $\mu$}
\end{figure}

@@

\begin{block}{Upper Bound On Mixing Time}
How effective Algorithm 1 is as a sampling method? Denote $\|\cdot\|_{\mathrm{TV}}$ the TV norm and $P^t(\bx^0)$ the density of $\bx^t$ starting from $\bx^0$. Define its mixing time to be 
\[
\tau_{\mathrm{mix}} \triangleq \min\{t|\max_{\bx^0}\|P^t(\bx^0) - p\|_{\mathrm{TV}}\leq 1/4\}.
\]
Suppose $\tau_{\bx^0}$ is the stopping time when the algorithm converges to global minimum starting from $\bx^0$, we might be able to have a upper bound for $\tau_{\mathrm{mix}}$.
\[
\tau_{\mathrm{mix}} \leq 4 \max_{\bx^0}\E \tau_{\bx^0}.
\]
So when SGD converges fast, it will also be efficient as a sampling method.
\end{block}

@@

\begin{itemize}
\item Proposed fast SGD sampler for posterior distributions when computing the likelihood using full data is intensive
\item Proved accurate stationary distribution based on oracle results
\item Established connection between SGD and maximize \emph{a posteriori} (MAP)
\item Derived upper bound on mixing time
\item Future work: Finite sample rates of convergence for the mixing time
\end{itemize}

@@

\begin{block}{Contact Information}
